%-------------------------
% Resume in Latex
% Author : Solomon Chan
% Based on template by Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Solomon Chan} \\ \vspace{1pt}
    \small \textit{(Legal name: Chan Ka Shing)} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} {55457456}
    $|$
    \faAt \hspace{.5pt} \href{mailto:kon98126157@yahoo.com.hk}{kon98126157@yahoo.com.hk}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/chan-ka-shing-511246259/}{LinkedIn}
\end{center}



%----------- SUMMARY -----------

\section{Summary}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        Full-Stack Developer with nearly 2 years of experience building web applications using modern frameworks (React, Node.js). Assisted in developing and maintaining a high-performance restaurant and shopping ordering system, e-commerce data crawlers, and logistics API integrations. Passionate about writing clean, efficient code to solve real-world problems.
    }}
  \resumeSubHeadingListEnd



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Hong Kong Baptist University}{Hong Kong}
      {Bachelor of Social Sciences (Honours) in Media and Social Communication}{Sep 2021 \textbf{--} Sep 2023}

    \resumeSubheading
      {Community College of City University}{Hong Kong}
      {Associate's degree, Creative Media Production}{Sep 2019 \textbf{--} Sep 2021}

  \resumeSubHeadingListEnd



%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Ntuple Global Limited}{Hong Kong}
      {Web Developer}{Nov 2022 \textbf{--} Sep 2024}
        \resumeItemListStart
            \resumeItem{Work Arrangement: Part-time (Nov 2022 - Aug 2023, 10 months, 2 days/week while completing studies), then Full-time (Sep 2023 - Aug 2024, 1 year, 5 days/week, Hybrid Work Model).}
            \resumeItem{Provided comprehensive full-stack web development services for company clients, delivering scalable and efficient solutions.}
            \resumeItem{Integrated logistics APIs for real-time shipment tracking, improving operational efficiency and customer visibility.}
            \resumeItem{Maintained and enhanced online ordering platform with payment gateway integration, ensuring secure and reliable transaction processing.}
            \resumeItem{Built an electronic commerce shipment tracking crawler portal to monitor and aggregate logistics data from multiple sources.}
            \resumeItem{Developed customized websites for corporate clients, tailored to specific business requirements and user needs.}
        \resumeItemListEnd

    \resumeSubheading
      {SYNNEX}{Hong Kong}
      {Part-time Data Entry}{Jan 2019 \textbf{--} Jan 2020}

  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

        \textbf{Programming Languages:}{ Java, JavaScript, TypeScript, C++, CSS, HTML, Python, PHP} \\ \vspace{3pt}

        \textbf{Frameworks:}{ React.js, Node.js, Next.js} \\ \vspace{3pt}

        \textbf{Databases:}{ MySQL, MongoDB} \\ \vspace{3pt}

        \textbf{Certifications:}{ Microsoft Office Specialist (MOS) Expert - Microsoft Office Excel 2010 Expert} \\ \vspace{3pt}

        \textbf{Languages:}{ Chinese (Cantonese), Chinese (Mandarin), English} \\ \vspace{3pt}

    }}
  \resumeSubHeadingListEnd



%----------- PROJECT EXPERIENCE -----------

\section{Project Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Logistics Integration Portal} $|$ \emph{\href{https://pacificstargp.com/}{pacificstargp.com}}}{}
      \resumeItemListStart
        \resumeItem{Integrated with different logistics companies API for helping the company print logistics orders.}
        \resumeItem{Enabled customers to place orders directly from the website, streamlining order management processes.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Beauty Questionnaire Website}}{}
      \resumeItemListStart
        \resumeItem{Developed a questionnaire website for beauty websites to collect customer preferences and feedback.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Online Ordering System} $|$ \emph{\href{https://dev.tasty-onlineorder.com/Home}{Tasty Online Order}} (Contributed)}{}
      \resumeItemListStart
        \resumeItem{Contributed to the development of an online ordering system for restaurants and food services.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{E-commerce Logistics Monitoring System} (Contributed)}{}
      \resumeItemListStart
        \resumeItem{Built a web scraper to monitor Hong Kong online shopping platform logistics statuses in real-time.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{TraxComm Staff Login System} (Contributed)}{}
      \resumeItemListStart
        \resumeItem{Participated in developing TraxComm's staff authentication and login system.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \item{References available upon request.}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
